---
title: "Interim Deliverable -1"
author: "Danielle Simms, Serena Shen, Runjie Lu and Ye Chen"
date: "9/24/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown 

#1A. WHAT IS PILGIRM BANK'S DATA PROBLEM?
### There is no data before 1999 about the use of online banking, therefore there is nothing on which to base future projection of online banking.

#1B. WHAT IS THE FINAL MANAGERIAL OBJECTIVE?
##Overall, the objective is to determine if online banking should be incorporated as part of the banking structure.
###CONSIDER:
####a. adding new channels will incur structural costs; would including online banking be worth it?
####b. should people be discouraged (through fees) or encouraged (discounts/rebates) for using online banking?
####c. are those who use online banking more likely to stay? (retention of customers)
####d. are those who use online banking more profitable?
####e. are those who use online channels and electronic bill pay more likely to stay?

#2.DESCRIBE THE MEASUREMENT TYPES OF EACH VARIABLE.
##a. ANNUAL PROFIT - what profit does this customer generate for the bank? (RATIO)
##b. ONLINE USAGE - does this customer use online banking? (NOMINAL; YES/NO)
##c. AGE BUCKET - what age is this customer? (ORDINAL)
###Grouped By: <15, 15-24, 25-34, 35-44, 45-54, 55-65, >65
##d. INCOME BUCKET - how much money doees this customer make/what is the income?
###Grouped By: <$15,000, $15,000-$19,999, $20,000-$29,999, $30,000-$39,999, $40,000-$49,999, $50,000-$74,999, $75,000-$99,999, $100,000-$124,999, >$125,000
####NOTE THAT: value jumps from increments of $10,000 to increments of $25,000 after $500,00 bracket
##e. TENURE - how long has this customer has been using this bank? (RATIO)
##f. GEOGRAPHIC REGION - where does this customer live?
###Distrcit is designated by 1100, 1200, and 1300

#4. HOW DO YOU HANDLE MISSING DATA IN THIS DATASET?
##a. decided to test the significance of the missing data to determine if the customers that have missing data should be excluded from analysis.
##b. utilized a t-test to determine that the data is important thus must be considered in the analysis. 
```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
