---
title: "Interim Deliverable -1"
author: "Danielle Simms, Serena Shen, Runjie Lu and Ye Chen"
date: "9/24/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown 

#1A. WHAT IS PILGIRM BANK'S DATA PROBLEM?
### There is no data before 1999 about the use of online banking, therefore there is nothing on which to base future projection of online banking.

#1B. WHAT IS THE FINAL MANAGERIAL OBJECTIVE?
##Overall, the objective is to determine if online banking should be incorporated as part of the banking structure.
###CONSIDER:
####a. adding new channels will incur structural costs; would including online banking be worth it?
####b. should people be discouraged (through fees) or encouraged (discounts/rebates) for using online banking?
####c. are those who use online banking more likely to stay? (retention of customers)
####d. are those who use online banking more profitable?
####e. are those who use online channels and electronic bill pay more likely to stay?

#2.DESCRIBE THE MEASUREMENT TYPES OF EACH VARIABLE.
##a. ANNUAL PROFIT - what profit does this customer generate for the bank? (RATIO)
##b. ONLINE USAGE - does this customer use online banking? (NOMINAL; YES/NO)
##c. AGE BUCKET - what age is this customer? (ORDINAL)
###Grouped By: <15, 15-24, 25-34, 35-44, 45-54, 55-65, >65
##d. INCOME BUCKET - how much money doees this customer make/what is the income?
###Grouped By: <$15,000, $15,000-$19,999, $20,000-$29,999, $30,000-$39,999, $40,000-$49,999, $50,000-$74,999, $75,000-$99,999, $100,000-$124,999, >$125,000
####NOTE THAT: value jumps from increments of $10,000 to increments of $25,000 after $500,00 bracket
##e. TENURE - how long has this customer has been using this bank? (RATIO)
##f. GEOGRAPHIC REGION - where does this customer live?
###Distrcit is designated by 1100, 1200, and 1300

#4. HOW DO YOU HANDLE MISSING DATA IN THIS DATASET?
##a. decided to test the significance of the missing data to determine if the customers that have missing data should be excluded from analysis.
##b. utilized a t-test to determine that the data is important thus must be considered in the analysis. (CODE 1)
###NULL HYPOTHESIS: The missing data points are not significant.
###ALTERNATE HYPOTHESIS: The missing data points are significant.
###Given the p-value of 9.79e-11 (< 0.05), t-statstic of -6.47 (absolute value > 1.96), and the 95% confidence interval does not include 0, we can reject the null hypothesis and therefore must consider missing values within the analysis.
##c. determined that the data needs to be replaced so that it can be useful in analysis; a pivot table should be produced to determine which paired variables appear most often together to replace the missing data, ie; if a profitablity is within the range of -60 to -50 and district 1200, the age of the customer is likely in the age bucket of 2.
###the pivot table was not produced for this deliverable due to time constraints.
```{r cars}
###< CODE 1. CONFIDENCE INTERVERAL >
pcData = read.csv("PilgrimCaseData.csv")
####pcData[!complete.cases(pcData),]
#####listAge = pcData$X9Age
#####listAge <- listAge[!is.na(listAge)]viewmean
listProfit = pcData$X9Profit
mean(listProfit)
listAge_Profit <- matrix(c(pcData$X9Age,pcData$X9Inc,pcData$X9Profit), ncol = 3)
listAge_Profit_NoNA = listAge_Profit[!is.na(listAge_Profit[,1]),]
listAge_Profit_NoNA = listAge_Profit_NoNA[!is.na(listAge_Profit_NoNA[,2]),]
listAge_Profit_NoNA = listAge_Profit_NoNA[!is.na(listAge_Profit_NoNA[,1]),]
###temp = listAge_Profit_NoNA[,2]
View(listAge_Profit_NoNA)
length(listAge_Profit_NoNA)
mean_WNA = mean(listAge_Profit[,3])

mean_NoNA = mean(listAge_Profit_NoNA[,3])
sd_NONA = sd(listAge_Profit_NoNA[,3])
size_NoNA = length(listAge_Profit_NoNA) / 3
var_NoNA = var(listAge_Profit_NoNA[,3])
####error_NoNA <- qt(0.975,df=size_NoNA-1)*sd_NONA/sqrt(size_NoNA)

#### t = (mean_NoNA - mean_WNA) / (sd_NONA/sqrt(size_NoNA))
t.test(listAge_Profit[,3],listAge_Profit_NoNA[,3],paired = FALSE)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
